DeepSphere: a graph-based spherical CNN

### 2019-11-14 main.tex
HealPix -> HEALPix

% 3.0) explain how we obtained the figures
In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \citet{khasanova2017sphericalcnn}.
The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.

@@

% \nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$. As the $\S^2$ is of dimension $2$, $\alpha$ cannot be larger than $\linefrac{1}{2}$. If we put that into the theorem, we obtain that $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$. I think this is important, because we can still have convergence even if we do not have perfect patches... Please confirm ASAP, so we can update the Proposition and the text bellow. For HealPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}

>>>>

% 3.0) explain how we obtained the figures
In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \citet{khasanova2017sphericalcnn}.
The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the HEALPix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.

@@

% \nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$. As the $\S^2$ is of dimension $2$, $\alpha$ cannot be larger than $\linefrac{1}{2}$. If we put that into the theorem, we obtain that $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$. I think this is important, because we can still have convergence even if we do not have perfect patches... Please confirm ASAP, so we can update the Proposition and the text bellow. For HEALPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}
